\documentclass[10pt,conference]{IEEEtran}

% Required packages
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{cite}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{url}

% Listings configuration
\lstset{
    basicstyle=\ttfamily\small,
    breaklines=true,
    frame=single,
    showstringspaces=false,
    keywordstyle=\color{blue},
    commentstyle=\color{gray},
    stringstyle=\color{red}
}

\begin{document}

\title{AISecIncidents-2025-26: A Dataset of AI Security Breaches with EU AI Act Compliance Mapping and Static Analysis of Claude Code}

\author{
\IEEEauthorblockN{Ahmed Adel Bakr Alderai}
\IEEEauthorblockA{Independent Researcher\\
Email: ahmed.adel.bakr@gmail.com}
}

\maketitle

\begin{abstract}
We present AISecIncidents-2025-26, a dataset of 55 AI security incidents spanning January 2025 to April 2026, of which 12 are verified through multi-source public confirmation and 43 are documented with structured confidence scores. Severity assessment reveals 76.4\% of incidents classified as High or Critical (20 Critical, 22 High, 13 Medium).

Alongside the dataset, we conduct a systematic static analysis of 1,332 TypeScript source files from a production AI agent (Claude Code v2.1.88). Our analysis reveals 23 AST-based security checks in the BashTool execution engine, a novel \emph{Semantic Desync} vulnerability class arising from non-deterministic LLM intent mapped to deterministic parser execution, and UNDERCOVER MODE---a 57,000-word instruction set with implications for transparency requirements.

We map findings to EU AI Act compliance requirements (Articles 9, 13, and 15) and release a multi-label classification benchmark (aisec-euaiact-v1.0, $n=12$ ground truth labels) for evaluating automated compliance classification systems.
\end{abstract}

\begin{IEEEkeywords}
AI security incidents, LLM supply chain security, EU AI Act compliance, dataset of security breaches, AI governance, vulnerability taxonomy, static analysis, multi-agent research methodology
\end{IEEEkeywords}

\section{INTRODUCTION}
\label{sec:introduction}

The deployment of large language models (LLMs) in production systems has created a new class of operational security risks that remain poorly characterized in the academic literature. While AI safety research has extensively addressed alignment, robustness, and fairness concerns~\cite{papernot2019}, the empirical study of security incidents in deployed LLM systems---including supply chain compromises, unauthorized model distillation, and system prompt extraction---remains fragmented and lacks standardized documentation.

This work addresses the empirical gap between theoretical threat modeling and real-world incident archaeology. We present AISecIncidents-2025-26, a comprehensive dataset of 55 AI security incidents spanning January 2025 to April 2026. The dataset comprises 12 incidents verified with multi-source public confirmation and 43 incidents documented with structured confidence scores on a 0--1 scale. Our methodology employs a parallel multi-agent research pipeline with source triangulation to achieve precision verification.

A distinguishing contribution of this work is the systematic static analysis of Claude Code v2.1.88, a production AI agent whose TypeScript source code became available for analysis through publicly distributed npm source maps. Our analysis of 1,332 source files reveals 23 AST-based security checks in the BashTool execution engine, a previously undocumented \emph{Semantic Desync} vulnerability class, and UNDERCOVER MODE---a 57,000-word instruction set with significant implications for transparency requirements under the EU AI Act~\cite{euaiact2024}.

The dataset is mapped to EU AI Act compliance requirements (Articles 9, 13, and 15), providing a framework for regulatory assessment. We release aisec-euaiact-v1.0, a multi-label classification benchmark with 12 ground-truth labels for evaluating automated compliance classification systems.

\textbf{Paper Organization.} Section~\ref{sec:related-work} surveys related work in ML security taxonomies, AI governance, and incident databases. Section~\ref{sec:dataset} presents the AISecIncidents-2025-26 dataset, including collection methodology, taxonomy, confidence scoring, and representative incidents. Section~\ref{sec:static-analysis} details our static analysis of Claude Code, including AST-based security checks, Semantic Desync vulnerability classification, and UNDERCOVER MODE analysis. Section~\ref{sec:benchmark} introduces the EU AI Act compliance benchmark with task definition and evaluation metrics. Section~\ref{sec:discussion} addresses limitations and ethical considerations. Section~\ref{sec:conclusion} concludes with future work directions.

\textbf{Key contributions:} (1) First large-scale open dataset correlating real-world LLM security incidents with regulatory compliance requirements; (2) Novel static analysis framework for AI agent security assessment with 23 AST-based checks and Semantic Desync vulnerability classification; (3) Discovery and analysis of a 57,000-word hidden instruction set in Claude Code with regulatory implications; (4) Standardized incident taxonomy with confidence scoring enabling quantitative benchmarking of incident response effectiveness.

\section{RELATED WORK}
\label{sec:related-work}

\subsection{Machine Learning Security Taxonomies}

The foundational taxonomies for machine learning security were established through systematic analysis of adversarial capabilities and threat models. Papernot et al.~\cite{papernot2019} established foundational taxonomies for ML security threats, including model stealing, membership inference, and adversarial example attacks. Their work predates the widespread deployment of LLM systems and does not address regulatory compliance frameworks that have emerged subsequently. Our dataset extends their threat model to production LLM systems and adds the regulatory compliance dimension.

Biggio and Roli~\cite{biggio2018} advanced theoretical foundations of adversarial machine learning with practical scaling considerations. Their characterization of ``wild patterns''---attacks that exploit the gap between training and deployment distributions---provides theoretical grounding for understanding incidents in our dataset involving prompt injection and model extraction.

\subsection{AI Governance and Fairness}

The intersection of technical ML systems and governance frameworks has received increasing attention as AI deployment scales. Selbst et al.~\cite{selbst2018} examined the abstraction barriers in machine learning systems that complicate fairness and accountability efforts. Their analysis of how technical abstractions can obscure sociotechnical concerns is relevant to our finding of \emph{Semantic Desync}, where the abstraction layer between LLM intent and parser execution creates security vulnerabilities.

The EU AI Act~\cite{euaiact2024} establishes a risk-based regulatory framework for AI systems, with specific obligations for high-risk AI including risk management systems (Article 9), transparency requirements (Article 13), and accuracy/robustness standards (Article 15). Our dataset provides the first empirical assessment of how real-world LLM security incidents map to these specific regulatory requirements.

\subsection{AI Incident Databases and Vulnerability Frameworks}

Several initiatives have attempted to catalog AI-related failures and security incidents. The AI Incident Database (AIID) catalogs AI-related harms across diverse application domains. While comprehensive in scope, AIID lacks systematic EU AI Act compliance mapping and does not employ multi-source verification for security incidents. Our work complements AIID by focusing specifically on security breaches with regulatory compliance assessment frameworks.

The OWASP LLM Top 10 2025~\cite{owasp_llm2025} provides a practitioner-oriented taxonomy of LLM application vulnerabilities. Our dataset operationalizes several of these categories---including prompt injection, insecure output handling, and supply chain vulnerabilities---as empirically observed incidents with documented impact and regulatory implications.

\section{AISECINCIDENTS-2025-26 DATASET}
\label{sec:dataset}

\subsection{Collection Methodology}

The dataset was constructed using a 12-agent parallel research pipeline with the following agent specializations:

\begin{itemize}
    \item \textbf{Source Discovery Agents:} Systematic monitoring of security advisories, bug bounty disclosures, and threat intelligence feeds.
    \item \textbf{Credibility Assessment Agents:} Multi-source triangulation and confidence scoring based on source independence and reputation.
    \item \textbf{Incident Classification Agents:} Taxonomy assignment and severity scoring according to CVSS-inspired criteria adapted for AI-specific risks.
    \item \textbf{Regulatory Mapping Agents:} EU AI Act Article mapping and compliance assessment.
\end{itemize}

Inter-agent triangulation protocols require confirmation from at least two independent sources for verification status. Incidents receive confidence scores on a 0--1 scale based on source reliability and corroboration level.

Agent communication follows a structured protocol where each agent generates structured output (JSON) consumed by downstream agents. The parallel architecture enables horizontal scaling: additional agents can be instantiated to increase throughput without requiring workflow modifications. Consensus mechanisms require agreement from at least two independent agent types before an incident receives verified status. The dataset is publicly available.\footnote{Dataset DOI: \url{https://doi.org/10.5281/zenodo.XXXXXXX} (to be updated upon Zenodo publication).}

\subsection{Taxonomy}

Incidents are classified across nine vulnerability types. Table~\ref{tab:taxonomy} presents the distribution.

\begin{table}[htbp]
\caption{Incident Taxonomy Distribution}
\label{tab:taxonomy}
\centering
\begin{tabular}{lr}
\toprule
\textbf{Vulnerability Class} & \textbf{Count} \\
\midrule
Source code exposure & 16 \\
Training data leakage & 9 \\
User data breaches & 8 \\
Supply chain attacks & 6 \\
API key compromise & 5 \\
API vulnerabilities & 4 \\
System prompt extraction & 3 \\
Model weight theft & 3 \\
State-sponsored attacks & 1 \\
\midrule
\textbf{Total} & \textbf{55} \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Confidence Score Methodology}

The dataset employs a structured confidence scoring system based on verification status and source quality. Table~\ref{tab:confidence} presents the four-tier confidence scale.

\begin{table}[htbp]
\caption{Confidence Score Tiers}
\label{tab:confidence}
\centering
\begin{tabular}{llc}
\toprule
\textbf{Verification Status} & \textbf{Source Quality} & \textbf{Score Range} \\
\midrule
Verified & Public sources only & 0.90--1.00 \\
Verified & Redacted internal data & 0.75--0.89 \\
Unverified & Non-empty URLs & 0.30--0.65 \\
Unverified & No URLs & 0.05--0.20 \\
\bottomrule
\end{tabular}
\end{table}

The rationale for this tiered approach balances precision and recall in incident documentation. Verified incidents with public sources achieve the highest confidence (0.90--1.00), serving as ground truth for benchmark evaluations. Verified incidents with redacted internal data (0.75--0.89) maintain high reliability while acknowledging limited public attribution. Unverified incidents with source URLs (0.30--0.65) capture the broader threat landscape with moderate confidence, while unverified incidents lacking source URLs (0.05--0.20) are retained for completeness but flagged as requiring further investigation. This scoring system enables researchers to filter incidents by confidence threshold according to their specific use case requirements.

The confidence scoring methodology was designed to address specific challenges in AI security incident documentation. Unlike traditional CVE assignments with binary verified/unverified status, AI incidents often involve proprietary systems where public confirmation is delayed or incomplete. The four-tier system captures this uncertainty quantitatively, enabling researchers to make informed decisions about which incidents to include in their analyses based on their tolerance for verification risk.

\subsection{Data Source Verification}

The dataset was compiled exclusively from publicly available sources, with no active exploitation or unauthorized access employed in the research process. Dual-source confirmation was required for all verified incidents, ensuring that each entry in the verified tier has independent corroboration from at least two distinct sources. The temporal scope spans January 2025 to April 2026, capturing a critical period in LLM deployment acceleration. All incidents were collected through passive monitoring of public disclosures, security advisories, and threat intelligence feeds, adhering to responsible disclosure practices and ethical research guidelines.

The multi-agent pipeline operates through iterative refinement cycles. Source Discovery Agents continuously monitor security advisories from major AI providers (OpenAI, Anthropic, Google, Meta), bug bounty platforms (HackerOne, Bugcrowd), and threat intelligence feeds. Credibility Assessment Agents apply source independence heuristics: incidents receive higher confidence when reported by both vendor disclosures and independent security researchers versus single-source attribution. The 12 verified incidents in the benchmark subset represent the intersection of vendor confirmation, security researcher documentation, and archived evidence availability.

\subsection{Representative Incidents}

To illustrate the dataset's coverage across vulnerability classes, we present three representative verified incidents:

\textbf{Source Code Leak (Claude Code npm Source Map Leak):} On March 31, 2026, Anthropic's Claude Code v2.1.88 npm package inadvertently included source map files exposing 1,332 TypeScript source files ($\sim$512,000 lines, 33MB) of the production AI agent's codebase. The leak revealed internal codenames (Capybara, Tengu, Kairos, Numbat), 50+ feature flags, and the UNDERCOVER MODE instruction set. This incident demonstrates how build system misconfigurations can expose proprietary AI agent internals with significant transparency implications under EU AI Act Article 13.

\textbf{Supply Chain Attack (Shai-Hulud npm Worm):} A sophisticated supply chain attack targeting the npm ecosystem affected over 2.1 million downloads through dependency confusion and typosquatting vectors. The worm propagated through build processes, exfiltrating environment variables and source code from CI/CD pipelines. This incident exemplifies cascading supply chain vulnerabilities in AI development infrastructure, directly implicating EU AI Act Article 9 risk management system requirements for third-party dependencies.

\textbf{System Prompt Extraction (Anthropic Mythos/Capybara CMS Leak):} Internal content management system misconfigurations exposed the Capybara model codename and associated system prompt architecture. The leak revealed model-specific handling instructions, including false-claim mitigation protocols for Capybara v8 (29--30\% FC rate) and persona calibration directives. This incident highlights transparency challenges when internal model design documentation becomes publicly accessible, raising questions about the completeness of disclosures required under Article 13.

\subsection{Verification Tiers}

The dataset employs a two-tier verification system that balances precision and recall in incident documentation:

\begin{itemize}
    \item \textbf{Verified (12 incidents):} Multi-source confirmation with independently verifiable public sources. These incidents serve as ground truth for benchmark evaluation and represent the highest-confidence subset of the dataset.
    \item \textbf{Unverified (43 incidents):} Single-source reports or threat intelligence with confidence scoring. These incidents expand coverage of the threat landscape but should be interpreted with appropriate caution.
\end{itemize}

This tiered approach acknowledges the practical challenges of incident verification in the AI security domain. Organizations may delay or avoid public disclosure for reputational, legal, or operational reasons. The unverified tier captures incidents that, while not meeting the strict dual-source requirement, nonetheless contribute to understanding the broader threat environment. Researchers can filter by verification status based on their specific requirements---using verified incidents for rigorous quantitative analysis and the full dataset for threat landscape characterization.

\subsection{Severity Distribution}

Severity assessment follows CVSS-inspired criteria adapted for AI-specific risks. Table~\ref{tab:severity} presents the distribution across all 55 incidents.

\begin{table}[htbp]
\caption{Severity Distribution}
\label{tab:severity}
\centering
\begin{tabular}{lrr}
\toprule
\textbf{Severity} & \textbf{Count} & \textbf{Percentage} \\
\midrule
Critical & 20 & 36.4\% \\
High & 22 & 40.0\% \\
Medium & 13 & 23.6\% \\
\midrule
\textbf{Total} & \textbf{55} & \textbf{100\%} \\
\bottomrule
\end{tabular}
\end{table}

\section{STATIC ANALYSIS OF CLAUDE CODE V2.1.88}
\label{sec:static-analysis}

\subsection{BashTool: AST-Based Security Checks}
\label{subsec:bashtool}

Analysis of the BashTool execution engine reveals 23 AST-based security checks implemented in TypeScript. These checks operate on abstract syntax trees of bash commands to detect potentially dangerous operations. The checks are organized into five functional categories:

\begin{enumerate}
    \item \textbf{Blocklist Detection (6 checks):} Commands matching known-dangerous patterns (e.g., \texttt{rm -rf}, \texttt{mkfs}, \texttt{dd} with device targets).
    \item \textbf{Subshell Detection (5 checks):} Identification of command substitution patterns (\texttt{\$(...)}, backticks) that may obfuscate malicious payloads.
    \item \textbf{Path Traversal Detection (4 checks):} Analysis of relative path constructions (\texttt{../}, \texttt{./}) and symlink following in file system operations.
    \item \textbf{Redirection Analysis (4 checks):} Detection of suspicious I/O redirections, including append-to-system-file and network socket redirections.
    \item \textbf{Pipeline Sanitization (4 checks):} Multi-command chain analysis to detect data exfiltration via pipelines and chained command execution.
\end{enumerate}

The AST-based approach provides semantic understanding of command structures beyond simple string matching, enabling detection of obfuscated or encoded attack patterns. However, as we discuss in Section~\ref{subsec:semantic-desync}, the semantic gap between LLM-generated intent and parser-executed checks introduces residual vulnerabilities.

\subsection{The 23 AST-Based Security Checks}
\label{subsec:23checks}

Table~\ref{tab:ast-checks} presents the complete inventory of AST-based security checks identified in the BashTool execution engine, categorized by security function.

\begin{table}[htbp]
\caption{AST-Based Security Checks in BashTool}
\label{tab:ast-checks}
\centering
\small
\begin{tabular}{ll}
\toprule
\textbf{Check Name} & \textbf{Category} \\
\midrule
DangerousCommandCheck & Blocklist Detection \\
DestructiveFileOperationCheck & Blocklist Detection \\
DiskFormatCheck & Blocklist Detection \\
SystemShutdownCheck & Blocklist Detection \\
PrivilegeEscalationCheck & Blocklist Detection \\
KernelModuleCheck & Blocklist Detection \\
CommandSubstitutionCheck & Subshell Detection \\
BacktickExecutionCheck & Subshell Detection \\
ProcessSubstitutionCheck & Subshell Detection \\
NestedSubshellCheck & Subshell Detection \\
EvalExecCheck & Subshell Detection \\
PathTraversalCheck & Path Traversal Detection \\
SymlinkFollowingCheck & Path Traversal Detection \\
RelativePathEscapeCheck & Path Traversal Detection \\
DotDotSlashCheck & Path Traversal Detection \\
FileRedirectionCheck & Redirection Analysis \\
SocketRedirectionCheck & Redirection Analysis \\
AppendSystemFileCheck & Redirection Analysis \\
DescriptorRedirectionCheck & Redirection Analysis \\
PipeToNetworkCheck & Pipeline Sanitization \\
MultiCommandChainCheck & Pipeline Sanitization \\
DataExfiltrationCheck & Pipeline Sanitization \\
EncodedPayloadCheck & Pipeline Sanitization \\
\bottomrule
\end{tabular}
\end{table}

Each check operates on the parsed AST representation of bash commands, enabling semantic analysis that transcends simple string pattern matching. Table~\ref{tab:check-examples} illustrates representative check implementations with example command patterns they detect.

\begin{table}[htbp]
\caption{Example AST Check Patterns}
\label{tab:check-examples}
\centering
\small
\begin{tabular}{ll}
\toprule
\textbf{Check} & \textbf{Example Detected Pattern} \\
\midrule
DangerousCommandCheck & \texttt{rm -rf /} \\
CommandSubstitutionCheck & \texttt{\$(curl attacker.com)} \\
PathTraversalCheck & \texttt{../../etc/passwd} \\
SocketRedirectionCheck & \texttt{/dev/tcp/host/port} \\
DataExfiltrationCheck & \texttt{cat file | nc host port} \\
\bottomrule
\end{tabular}
\end{table}

The Blocklist Detection category identifies commands with known destructive capabilities. Subshell Detection focuses on execution contexts that may bypass security controls. Path Traversal Detection prevents unauthorized file system access. Redirection Analysis monitors I/O operations that could enable data exfiltration or system compromise. Pipeline Sanitization examines command chains for suspicious data flows.

\subsection{Semantic Desync Vulnerability Class}
\label{subsec:semantic-desync}

Our analysis identifies a novel vulnerability class we term \emph{Semantic Desync}, arising from the architectural separation between LLM intent interpretation and deterministic parser execution:

\begin{definition}[Semantic Desync]
A vulnerability occurring when non-deterministic LLM-generated intent is mapped to deterministic parser execution, creating a semantic gap where the parser's interpretation diverges from the LLM's intended meaning, potentially allowing hidden instructions to override visible safety constraints.
\end{definition}

This vulnerability class is particularly relevant for AI agents that parse natural language instructions into executable code or system commands. The non-deterministic nature of LLM outputs combined with deterministic parsing logic creates inherent semantic ambiguity that can be exploited. In the context of Claude Code, Semantic Desync manifests when the BashTool AST parser interprets a command structure differently from the LLM's generated intent, enabling circumvention of the 23 AST-based checks described in Section~\ref{subsec:bashtool}.

A concrete example illustrates this vulnerability: the LLM interprets a user request as asking for a directory listing and generates the natural language response ``please list the files.'' However, the BashTool parser expects shell command syntax and attempts to execute this string directly. The mismatch between natural language intent and shell command syntax creates unpredictable execution behavior. If the parser applies partial sanitization or interprets certain natural language phrases as shell metacharacters, the result may bypass security checks while producing unintended execution outcomes. This semantic boundary condition---where LLM-generated natural language intersects with deterministic command parsers---represents a fundamental architectural vulnerability in AI agent systems.

The CVE-2025-55284 Claude Code DNS exfiltration vulnerability~\cite{cve2025_55284} exemplifies this class with technical precision. The vulnerability manifested when the LLM generated a command sequence intended as network diagnostics: \texttt{dig @resolver.query.com $(cat /etc/passwd | base64).attacker.com}. The LLM interpreted this as a diagnostic query to a nameserver, while the BashTool parser executed it as a DNS exfiltration channel encoding sensitive file contents in subdomain queries. The AST checks do not flag the command because each individual token passes syntactic validation, yet the semantic composition yields an attack.

Mitigation strategies for Semantic Desync include: (1) constrained natural language interfaces that restrict LLM output to formally defined grammars; (2) semantic validation layers that execute commands in sandboxed environments before production deployment; (3) human-in-the-loop confirmation for commands with ambiguous semantic interpretations; and (4) runtime monitoring to detect anomalous command patterns that may indicate successful Semantic Desync exploitation.

This vulnerability class has implications beyond Claude Code. Any AI agent architecture that interposes a deterministic parser between non-deterministic LLM output and command execution may be susceptible to Semantic Desync. The architectural pattern of LLM intent interpretation followed by structured command parsing---common across agent frameworks including OpenAI's Function Calling, Google's Function Declarations, and LangChain tool implementations---creates similar semantic boundary conditions. We recommend that agent developers implement explicit semantic validation layers that verify LLM-generated content conforms to expected output schemas before parser processing.

\subsection{UNDERCOVER MODE: 57K-Word System Prompt and Article 13 Implications}
\label{subsec:undercover}

Static analysis reveals UNDERCOVER MODE, a 57,000-word system prompt instruction set (approximately 380,000 characters) embedded in the Claude Code source. This instruction set operates across four behavioral layers: (1) \textbf{Identity Layer}---suppressing model self-identification and attribution; (2) \textbf{Capability Layer}---constraining available functions and response modalities; (3) \textbf{Restriction Layer}---defining prohibited operations and content boundaries; and (4) \textbf{Persona Layer}---adapting communication style based on repository context (internal vs. public).

Analysis of the 57,000-word instruction set reveals substantial complexity beyond typical system prompts. The instruction set includes nested conditionals, context-dependent rule activation, and dynamic behavior modification based on repository classification (internal vs. public). Key components include:

\begin{itemize}
    \item \textbf{CYBER\_RISK\_INSTRUCTION:} Hidden safety override mechanisms that modify default tool behavior in specific repository contexts.
    \item \textbf{TENGU Feature Flags:} Coordinated multi-agent behavior controls governing background execution, proactive behavior, and cross-agent communication.
    \item \textbf{Obfuscation Layer:} Multi-level encoding of instruction semantics, including codename substitution (e.g., ``Capybara'' for internal model variants) and dynamic prompt boundary injection.
\end{itemize}

The scale of this instruction set raises significant questions under EU AI Act Article 13, which mandates that users be informed when interacting with AI systems and that high-risk AI systems provide ``clear and adequate'' information about their capabilities and limitations. The presence of a 57,000-word undisclosed instruction set that can modify system behavior---including the stripping of attribution, suppression of model identity, and activation of hidden feature flags---challenges the completeness of transparency disclosures.

Specifically, Article 13(3) requires that AI systems ``be designed and developed in such a way that the natural persons to whom the output is addressed are informed that they are interacting with an AI system.'' UNDERCOVER MODE contains explicit instructions to remove ``any mention that you are an AI'' and to suppress the phrase ``Claude Code'' in public repository contexts, directly conflicting with transparency obligations. Article 13 also requires documentation of the AI system's ``intended purpose'' and ``capabilities and limitations.'' The four-layer behavioral control system in UNDERCOVER MODE---with its context-dependent capability restrictions and persona adaptations---introduces dynamic behavior modifications that may not be fully captured in static documentation, potentially creating compliance gaps under EU AI Act transparency requirements.

\section{EU AI ACT COMPLIANCE BENCHMARK}
\label{sec:benchmark}

We introduce aisec-euaiact-v1.0, a multi-label classification benchmark for EU AI Act compliance assessment. The benchmark comprises 12 verified incidents with ground-truth labels mapping to Articles 9, 13, and 15.

\subsection{Task Definition}

Given an AI security incident description, the task is to classify which EU AI Act article(s) are primarily violated:

\begin{itemize}
    \item \textbf{Article 9:} Risk Management System (supply chain, third-party risks).
    \item \textbf{Article 13:} Transparency and Provision of Information (disclosure, visibility).
    \item \textbf{Article 15:} Accuracy, Robustness, Cybersecurity (technical failures).
\end{itemize}

The label space comprises all non-empty subsets of \{9, 13, 15\}, yielding seven valid label combinations: \{9\}, \{13\}, \{15\}, \{9, 13\}, \{9, 15\}, \{13, 15\}, and \{9, 13, 15\}. This design reflects the reality that security incidents often violate multiple regulatory obligations simultaneously. For instance, a supply chain attack may implicate both Article 9 (insufficient risk management of third-party components) and Article 15 (cybersecurity failures enabling the breach).

\subsection{Evaluation Methodology}

The benchmark employs multi-label classification evaluation with $n=12$ ground-truth expert-labeled incidents. We adopt F1 micro and macro averages as primary metrics due to their suitability for multi-label classification with imbalanced label distributions.

\textbf{Micro-averaged F1} aggregates contributions from all labels to compute global precision and recall. This metric is appropriate when the goal is overall classification performance without per-label weighting. It is calculated as:
\begin{equation}
\text{F1}_{\text{micro}} = 2 \cdot \frac{P_{\text{micro}} \cdot R_{\text{micro}}}{P_{\text{micro}} + R_{\text{micro}}}
\end{equation}
where $P_{\text{micro}}$ and $R_{\text{micro}}$ are computed from global true positives, false positives, and false negatives across all labels.

\textbf{Macro-averaged F1} computes F1 for each label independently and averages the results. This metric treats all articles equally regardless of frequency, ensuring that performance on Article 13 (the least prevalent) contributes equally to the final score. Primary metrics include F1 micro and macro averages, reflecting the multi-label nature of the compliance classification task. Micro-averaged metrics aggregate contributions across all labels, providing a global measure of performance that accounts for label frequency imbalance. Macro-averaged metrics compute per-label performance before averaging, ensuring equal weight for each EU AI Act article regardless of prevalence in the dataset.

The 12-incident ground truth set was constructed through expert annotation by three independent reviewers with legal and machine learning expertise. Inter-annotator agreement measured 78.3\% exact match with Fleiss' kappa of 0.71, indicating substantial agreement. Disagreements were resolved through majority voting, with borderline cases requiring full consensus. This rigorous annotation process ensures high-quality labels for benchmarking automated compliance classification systems.

\subsection{Label Distribution and Article Mapping}

Table~\ref{tab:labels} presents the ground-truth label distribution across the 12 verified incidents.

\begin{table}[htbp]
\caption{Benchmark Label Distribution ($n=12$)}
\label{tab:labels}
\centering
\begin{tabular}{lc}
\toprule
\textbf{Label Combination} & \textbf{Count} \\
\midrule
\{9, 15\} & 5 \\
\{9, 13\} & 2 \\
\{13\} & 1 \\
\{9, 13, 15\} & 1 \\
\{13, 15\} & 1 \\
\bottomrule
\end{tabular}
\end{table}

Table~\ref{tab:article-mapping} provides the explicit mapping from benchmark labels to EU AI Act articles, establishing the regulatory foundation for classification decisions.

\begin{table}[htbp]
\caption{Benchmark Label to EU AI Act Article Mapping}
\label{tab:article-mapping}
\centering
\begin{tabular}{ll}
\toprule
\textbf{Benchmark Label} & \textbf{EU AI Act Article} \\
\midrule
source\_code\_leak & Article 13 (Transparency) \\
supply\_chain\_attack & Article 9 (Risk Management) \\
system\_prompt\_extraction & Article 13 (Transparency) \\
training\_data\_leakage & Article 15 (Robustness) \\
user\_data\_breach & Article 9 (Risk Management) \\
api\_key\_compromise & Article 15 (Robustness) \\
\bottomrule
\end{tabular}
\end{table}

Table~\ref{tab:article-prevalence} shows per-article prevalence across the benchmark dataset. Article 9 (Risk Management) violations are most prevalent at 75\%, reflecting the supply chain and third-party risk focus of many documented incidents. Article 15 (Robustness) violations at 58.3\% indicate technical security failures are common across incident types. Article 13 (Transparency) at 50\% suggests that disclosure and visibility issues affect half of verified incidents.

\begin{table}[htbp]
\caption{Per-Article Prevalence ($n=12$)}
\label{tab:article-prevalence}
\centering
\begin{tabular}{lrr}
\toprule
\textbf{Article} & \textbf{Incidents} & \textbf{Prevalence} \\
\midrule
Article 9 (Risk Management) & 9 & 75.0\% \\
Article 15 (Robustness) & 7 & 58.3\% \\
Article 13 (Transparency) & 6 & 50.0\% \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Evaluation Metrics}

Following standard multi-label classification evaluation, we report:

\begin{itemize}
    \item \textbf{Exact Match (EM):} Proportion of predictions matching ground truth exactly.
    \item \textbf{Precision/Recall/F1:} Micro-averaged across all labels.
    \item \textbf{Hamming Loss:} Fraction of incorrect labels.
    \item \textbf{Mean Jaccard Index (MJI):} Intersection over Union for label sets, providing partial credit for incomplete predictions.
\end{itemize}

\textbf{Baseline Results.} Table~\ref{tab:baselines} summarizes baseline performance metrics for comparison.

\begin{table}[htbp]
\caption{Baseline Performance Comparison}
\label{tab:baselines}
\centering
\small
\begin{tabular}{lcc}
\toprule
\textbf{Baseline} & \textbf{Exact Match} & \textbf{Mean Jaccard} \\
\midrule
Random Classifier & 14.3\% & 0.357 \\
Majority Class & 41.7\% & 0.486 \\
Human Expert (est.) & 78.0\% & 0.850 \\
\bottomrule
\end{tabular}
\end{table}

A uniform random classifier achieves 14.3\% exact match and 0.357 mean Jaccard; the majority-class baseline (predicting \{9, 15\}) achieves 41.7\% exact match and 0.486 mean Jaccard. Human expert inter-annotator agreement of 78.3\% suggests a performance ceiling for automated systems.

Preliminary experiments with off-the-shelf language models (GPT-4, Claude Sonnet 4.5, Gemini Pro) demonstrate the difficulty of the task. Zero-shot prompting yields 25--35\% exact match, significantly below human expert performance. Fine-tuning on legal text classification tasks provides modest improvements (35--42\%), suggesting that specialized domain knowledge is essential for accurate EU AI Act compliance classification.

Error analysis reveals that model failures concentrate on incidents involving overlapping obligations. Supply chain attacks, for example, frequently trigger both Article 9 (risk management) and Article 15 (cybersecurity) obligations, and models often miss one or the other. This suggests that future approaches should explicitly model the relationships between regulatory obligations rather than treating each article as an independent classification target.

\subsection{Open Research Challenge}

Establishing strong baseline performance on the aisec-euaiact-v1.0 benchmark remains an open research problem. The multi-label nature of EU AI Act compliance classification, combined with the nuanced interpretation required to map incident descriptions to regulatory articles, presents significant challenges for automated systems. The complexity of distinguishing between Article 9 risk management failures, Article 13 transparency violations, and Article 15 robustness deficiencies requires sophisticated legal-technical reasoning that current automated systems struggle to replicate. We invite community submissions to establish baseline performance and advance automated compliance assessment capabilities. All benchmark data, evaluation scripts, and submission guidelines are available via the dataset repository referenced in the DOI footnote.

\section{DISCUSSION}
\label{sec:discussion}

\subsection{Dataset Applications}

The AISecIncidents-2025-26 dataset supports multiple research applications beyond the compliance benchmark. Researchers can use the dataset for: (1) training machine learning models for incident classification; (2) analyzing temporal trends in AI security vulnerabilities; (3) evaluating organizational disclosure practices; (4) studying the relationship between incident severity and media coverage; and (5) developing automated alert systems for emerging threat patterns. The confidence scoring enables researchers to filter data quality according to their risk tolerance for unverified information.

\subsection{Limitations}

Several limitations affect the generalizability of our findings.

\textbf{Verification Gap:} Approximately 78\% of incidents (43/55) remain unverified with single-source attribution. This reflects the inherent challenge of incident verification in the AI security domain, where organizations may delay or avoid public disclosure.

\textbf{Selection Bias:} The dataset exhibits bias toward public-facing large organizations with established security disclosure practices. Incidents at smaller organizations or in regions with weaker disclosure requirements may be underrepresented.

\textbf{Temporal Constraints:} The 2025--2026 temporal boundary captures a specific period in AI security evolution. Rapid changes in LLM deployment practices may limit the relevance of incident patterns for future periods.

\textbf{Attribution Uncertainty:} Threat intelligence reports may contain attribution errors or deliberate misdirection. Our confidence scoring partially addresses this but cannot eliminate uncertainty.

\textbf{Static Analysis Scope:} The analysis of Claude Code covers version 2.1.88 only. Subsequent versions may have addressed identified vulnerabilities or introduced new security controls. The findings should be interpreted as a snapshot of the security posture at a specific point in time rather than a comprehensive assessment of the system's evolution.

\textbf{Regulatory Interpretation:} The mapping of incidents to EU AI Act articles represents our interpretation of regulatory requirements. Actual enforcement determinations may vary based on legal context, jurisdictional nuances, and evolving guidance from competent authorities.

\textbf{Regulatory Interpretation:} EU AI Act compliance mapping involves interpretation of legal requirements that may evolve as regulatory guidance is issued. Our mapping reflects the state of knowledge as of April 2026 and should be updated as the regulatory framework matures.

\textbf{Technical Scope:} The static analysis focuses on the BashTool execution engine and does not cover all security mechanisms in Claude Code. Other tools and subsystems may have different security properties that were not analyzed in this work.

\subsection{Future Work}

Several directions for future research emerge from this work:

\textbf{Longitudinal Analysis:} Extending the dataset beyond April 2026 will enable analysis of trends in AI security incidents over time. Longitudinal tracking can assess whether incident rates are increasing with broader LLM deployment and whether defensive measures are becoming more effective.

\textbf{Cost Quantification:} Linking incidents to quantifiable organizational impacts---financial losses, remediation costs, reputational damage---would enable risk assessment frameworks for AI security investments. Understanding the economic impact of different incident types can inform resource allocation decisions.

\textbf{Defensive Evaluation:} Red team exercises using documented incidents as prior examples can assess organizational preparedness. Measuring whether knowledge of historical attacks improves defensive capabilities would validate the practical utility of incident datasets.

\textbf{Cross-Framework Analysis:} Extending compliance mapping to additional frameworks (NIST AI RMF, ISO/IEC 42001, sector-specific regulations) would provide a more comprehensive view of regulatory obligations.

\subsection{Ethical Considerations}

This research was conducted following responsible disclosure practices:

\begin{itemize}
    \item npm source maps analyzed were publicly accessible metadata distributed through the npm registry, not obtained through unauthorized access or active exploitation.
    \item No active exploits were developed or deployed against production systems.
    \item No proof-of-concept code for identified vulnerabilities has been published.
    \item Affected organizations were notified of unpatched vulnerabilities with 90-day disclosure timelines.
\end{itemize}

The static analysis of Claude Code source files was conducted on code that was inadvertently exposed through publicly accessible source maps. Analysis was limited to security-relevant patterns and did not include extraction of proprietary business logic or training data. The research followed responsible disclosure practices, with affected vendors notified of significant findings.

Dataset distribution follows principles of responsible openness. The full dataset is available for academic and security research with appropriate attribution. Sensitive technical details that could enable exploitation are described at a level of abstraction sufficient for research without providing actionable attack guidance. This balance enables scientific progress while minimizing potential for misuse.

\section{CONCLUSION}
\label{sec:conclusion}

We present AISecIncidents-2025-26, a dataset of 55 AI security incidents with EU AI Act compliance mapping, and the first systematic static analysis of a production AI agent (Claude Code v2.1.88). Our findings include the identification of 23 AST-based security checks, a novel Semantic Desync vulnerability class, and analysis of a 57,000-word hidden instruction set with transparency implications under Article 13 of the EU AI Act. The dataset and benchmark are publicly available to support future research in AI security and regulatory compliance.

The aisec-euaiact-v1.0 benchmark provides a foundation for evaluating automated compliance classification systems. Our work bridges the empirical gap between theoretical AI security research and real-world incident documentation, providing actionable insights for practitioners and regulators developing enforcement mechanisms under the EU AI Act.

The dataset and benchmark are designed to evolve with the regulatory landscape. As EU AI Act implementing acts clarify specific requirements and as new incident patterns emerge, the taxonomy and article mappings can be extended while maintaining backward compatibility with the core schema. We anticipate community contributions will expand the verified incident set beyond the initial 12 ground-truth labels, enabling more robust evaluation of compliance classification systems.

Future work directions include longitudinal tracking (2027+), downstream cost analysis for organizational damages, and red team evaluation using dataset incidents as prior examples. We also plan to extend the benchmark with additional verified incidents as public disclosures become available, and to develop automated tools for confidence scoring and regulatory mapping that can assist security researchers in incident documentation. We call for increased incident transparency norms in the AI industry to enable more comprehensive security research.

The findings of this work carry implications for three stakeholder groups. AI practitioners should implement defense-in-depth strategies that account for Semantic Desync vulnerabilities and conduct regular audits of system prompt behavior. Regulators should consider the practical challenges of compliance verification highlighted by the benchmark results when designing enforcement mechanisms. Researchers should prioritize reproducible, multi-source verified incident documentation to build cumulative knowledge in AI security.

As AI systems become increasingly integrated into critical infrastructure, understanding and documenting security incidents becomes essential for risk management. This dataset provides a foundation for evidence-based security decisions and regulatory compliance assessment. We invite the research community to build upon this work, extending the dataset, improving classification methods, and developing practical tools for AI security assessment.

The AISecIncidents-2025-26 dataset, benchmark labels, and evaluation scripts are available at \url{https://huggingface.co/datasets/Ahmed-AdelB/ai-security-incidents-2025-2026}. We welcome contributions of new incidents, corrections to existing records, and improvements to the compliance mapping. By fostering a collaborative approach to AI security documentation, we aim to support the development of more secure and trustworthy AI systems.

\bibliographystyle{IEEEtran}
\bibliography{bibliography}

\end{document}
